sensiAnPaper1All

### 2016-02-11 sensiAnPaper1All.Rmd
changing scenarios

  #nScenarios <- 10  
  #nScenarios <- 100
  nScenarios <- 1000

@@

  ## save results objects as rda for re-use
  save(listOutMix, file=paste0(outFolder,'listOutMix.rda'))
  save(listOutI1, file=paste0(outFolder,'listOutI1.rda'))
  save(listOutI2, file=paste0(outFolder,'listOutI2.rda'))

  save(listOutMix, file=paste0(outFolder,'listOutMix_ex1000.rda'))
  save(listOutI1, file=paste0(outFolder,'listOutI1_ex1000.rda'))
  save(listOutI2, file=paste0(outFolder,'listOutI2_ex1000.rda'))

@@

```{r}
  ## to load previously saved runs
#   load(file=paste0(outFolder,'listOutMix_1000.rda'))
#   load(file=paste0(outFolder,'listOutI1_1000.rda'))
#   load(file=paste0(outFolder,'listOutI2_1000.rda'))

  load(file=paste0(outFolder,'listOutMix_ex1000.rda'))
  load(file=paste0(outFolder,'listOutI1_ex1000.rda'))
  load(file=paste0(outFolder,'listOutI2_ex1000.rda'))

@@

### do tree analysis
```{r, eval=TRUE}
  require(rpart.plot)

@@

  #convert predictor columns back to numeric
  #following this above : replace 0s & 1s with mixture/sequence to make plot clearer
  filter <- !substr(names(treeInput),1,6) %in% 'better'
  treeInput[,filter] <- lapply(treeInput[,filter],as.numeric) 
  filter <- !filter
  treeInput[,filter] <- lapply(treeInput[,filter],as.factor)

  #create string with predictor names in
  treePredictorString <- paste(treePredictors, collapse="+")

@@

### investigating response of time-to-resistance to individual input parameters
### (while they all are varying so it may not work well)
```{r, eval=TRUE}

  #uses ggInput calculated in earlier chunk

  #first needs to transpose rows to cols
  #ggInput_T <- t(ggInput)

  #function to transpose and add strategy column with the passed value
  #also add on the input columns  
  addStrategyColumn <- function(x, value, inputs){
    x <- as.data.frame( t(x) )
    x$strategy <- value
    #transpose inputs
    inputs <- as.data.frame( t(inputs) )
    #cbind onto the outputs
    x <- cbind(inputs,x)
    x
  }

  resistPointsI1_T <- addStrategyColumn(resistPointsI1,"insecticide 1",ggInput) 
  resistPointsI2_T <- addStrategyColumn(resistPointsI2,"insecticide 2",ggInput)   
  resistPointsSeq_T <- addStrategyColumn(resistPointsSeq,"Sequential",ggInput) 
  resistPointsMix1_T <- addStrategyColumn(resistPointsMix1,"Mixture 1",ggInput) 
  resistPointsMix2_T <- addStrategyColumn(resistPointsMix2,"Mixture 2",ggInput) 
  resistPointsMix3_T <- addStrategyColumn(resistPointsMix3,"Mixture 3",ggInput)

  ggInsOuts <- rbind( resistPointsI1_T, resistPointsI2_T, resistPointsSeq_T, 
                      resistPointsMix1_T, resistPointsMix2_T, resistPointsMix3_T)

  #ggplot(diamonds, aes(x=carat, y=price, color=cut)) + geom_point() + facet_wrap( ~ cut)

  #cool working!

  #this one shows no discernible pattern
  ggplot(ggInsOuts, aes(x=effectiveness_insecticide1, y=gen_cP0.5, color=strategy)) + geom_point() + facet_wrap( ~ strategy) + geom_smooth()

  #doing; for all inputs
  names_inputs <- names(ggInsOuts)[1:10]

  for(i in names_inputs)
  {
    x11()

    y <- 'gen_cP0.5'
    #color <- 'strategy'
    #coloring by exposure shows its effect even when other params are varying
    color <- 'exposure'

    print( ggplot(ggInsOuts, aes_string(x=i, y=y, color=color)) + 
             geom_point() + 
             facet_wrap( ~ strategy) + 
             geom_smooth(aes_string(x=i, y=y, color=NULL)) )
  }

  #can I facet by particular parameter ranges ?
  #or even subset the data for specific parameter ranges

>>>>

  nScenarios <- 3  
  #nScenarios <- 100
  #nScenarios <- 1000  
  #nScenarios <- 10000

@@

  ## save results objects as rda for re-use
  #save(listOutMix, file=paste0(outFolder,'listOutMix.rda'))
  #save(listOutI1, file=paste0(outFolder,'listOutI1.rda'))
  #save(listOutI2, file=paste0(outFolder,'listOutI2.rda'))

  save(listOutMix, file=paste0(outFolder,'listOutMix_ex2_10000.rda'))
  save(listOutI1, file=paste0(outFolder,'listOutI1_ex2_10000.rda'))
  save(listOutI2, file=paste0(outFolder,'listOutI2_ex2_10000.rda'))

#   save(listOutMix, file=paste0(outFolder,'listOutMix_ex2_3.rda'))
#   save(listOutI1, file=paste0(outFolder,'listOutI1_ex2_3.rda'))
#   save(listOutI2, file=paste0(outFolder,'listOutI2_ex2_3.rda'))

@@

```{r, eval=FALSE}
  ## to load previously saved runs
#   load(file=paste0(outFolder,'listOutMix_1000.rda'))
#   load(file=paste0(outFolder,'listOutI1_1000.rda'))
#   load(file=paste0(outFolder,'listOutI2_1000.rda'))

  load(file=paste0(outFolder,'listOutMix_ex2_10000.rda'))
  load(file=paste0(outFolder,'listOutI1_ex2_10000.rda'))
  load(file=paste0(outFolder,'listOutI2_ex2_10000.rda'))

@@

@@

### do tree analysis
```{r, eval=TRUE}

  require(rpart.plot)

  #convert predictor columns back to numeric
  #following this above : replace 0s & 1s with mixture/sequence to make plot clearer
  results_columns <- substr(names(treeInput),1,6) %in% 'better'
  input_columns <- !results_columns
  treeInput[,input_columns] <- lapply(treeInput[,input_columns],as.numeric) 
  treeInput[,results_columns] <- lapply(treeInput[,results_columns],as.factor)

  #create string with predictor names in
  #treePredictorString <- paste(treePredictors, collapse="+")
  treePredictorString <- paste(colnames(treeInput)[input_columns], collapse="+")

@@
